---
title: "Processing Results from the EI-ww model"
author: "Isaac H Goldstein"
date: today
format: html
editor: visual
---

## Overview

This document shows how to use `R` code to process MCMC samples from the EI-ww model generated in `Julia` to create dataframes used to summarise frequentist metrics and visualize results. This document combines code from `scripts/process_results/process_results_stc_ei_normal_newshedding.R` and `scripts/visualize_results/viz_uci_posterior_rt.R`.

## Install libraries

## Load libraries, choose simulation and seed

For a list of the meanings of the possible scenarios, see `vignettes/fit_ei_ww.qmd`. This document defaults to assuming `sim="G2` and `seed=1` as in the previous vignette.

```{r}
#| output: false
### Process Results stc ei normal for newshedding 
library(tidyverse)
library(tidybayes)
library(posterior)
library(fs)
source(here::here("src/utility_functions.R"))
# choose key frame based on if real or simulated data
real_data = TRUE
if (real_data == TRUE) {
  key_frame <- read_csv(here::here("data", "newshedding_data", "real_key.csv"))
} else {
  key_frame <- read_csv(here::here("data", "newshedding_data", "sim_key.csv"))
}
sim = "G2"
seed = 1

datafilename = key_frame %>% 
    filter(sim_num == sim) %>% 
    pull(obsdata_filename) %>% 
    unique() %>%
    as.character()
in_order_val = FALSE
```

## load posterior samples, calculate mcmc diagnostics

```{r}

# calculate MCMC diagnostics after burnin
gq_address <- paste0("results/stoch_conc_ei_normal/generated_quantities/generated_quantities_scenario", 
                     sim, 
                     "_seed", 
                     seed,
                     ".csv")

posterior_samples <- read_csv(here::here(gq_address)) %>%
  rename(.iteration = iteration,
         .chain = chain) %>%
  as_draws()

# choose which chains to keep
if (sim == 115 & seed == 88) {
  chain_list = c(1,3,4)
} else if (sim == 115 & seed == 40) {
  chain_list = c(1,3,4)
} else if (sim == 106 & seed == 26) {
  chain_list = c(1,2)
} else if (sim == 106 & seed == 88) {
  chain_list = c(1,2,3)
} else if (sim == "G1" & seed == 1){
  chain_list = c(1,2,4)
} else if (sim == "G2" & seed == 1) {
  chain_list = c(1,2,3)
} else {
  chain_list = c(1,2,3,4)
}
subset_samples <- subset_draws(posterior_samples, chain = chain_list)

mcmc_summary <- summarise_draws(subset_samples)
```

## create long format mcmc samples

This code creates two dataframes: one with the mcmc samples for non-time-varying parameters, the other quantiles of the time-varying parameters.

```{r}
posterior_gq_samples_all <- subset_samples  %>%
  pivot_longer(-c(.iteration, .chain)) %>%
  dplyr::select( name, value)


posterior_fixed_samples <- make_fixed_posterior_samples(posterior_gq_samples_all)
posterior_timevarying_quantiles <- make_timevarying_posterior_quantiles(posterior_gq_samples_all)

```

## create posterior predictive quantiles

This code creates quantiles for the posterior predictive for each day there was observed data

```{r}
post_pred_address <- paste0("results/stoch_conc_ei_normal/posterior_predictive/posterior_predictive_scenario",
                            sim,
                            "_seed",
                            seed,
                            ".csv")
post_pred <- read_csv(here::here(post_pred_address))

  simdata <- read_csv(here::here(datafilename)) %>%
    mutate(total_conc = 1)


post_pred_intervals <- make_post_pred_intervals(post_pred, simdata, in_order_val)
```

## Visualizing the posterior of Rt

Once the time-varying quantiles have been created, we can visualize them. In this vignette, we visualize the quantiles of the G2 community at UC Irvine.

```{r}
# create time crosswalks for visualizing compartment counts
uci_data <- read_csv(here::here("data", "uci_ww_data.csv"), 
                     show_col_types = FALSE)

G2_data <- uci_data %>% filter(place == "G2")

G2_param_change_times <- seq(lump_val, max(G2_data$new_time), by = lump_val)
G2_solve_times <- sort(union(unique(G2_data$new_time), G2_param_change_times))
G2_num_timepoints <- length(G2_solve_times)
G2_min_date <- min(G2_data$date) - ddays(1)
G2_time_crosswalk <- data.frame(time = 0:(G2_num_timepoints-1), 
                                 new_time = G2_solve_times) %>%
  mutate(date = G2_min_date + ddays(new_time),
         lump = floor((new_time)/lump_val))

# then we filter the time-varying quantiles dataframe for the Rt quantiles and visualize

G2_stc_rt_quantiles <- posterior_timevarying_quantiles %>%
  filter(name == "rt_t_values") %>%
  rename(lump = time) %>% 
  dplyr::select(lump, value, .lower, .upper, .width,.point, .interval) %>%
  right_join(G2_time_crosswalk, by = c("lump")) %>%
  dplyr::select(lump, new_time, date, value, .lower, .upper, .width) %>%
  distinct()

# visualize results
G2_stc_plot_posterior_rt <- G2_stc_rt_quantiles %>% 
  filter(lump >= 0) %>%
  ggplot(aes(x = date, y = value,  ymin = .lower, ymax = .upper)) +
  geom_lineribbon() +
  geom_hline(yintercept = 1, linetype = "dashed") +
  theme_bw() +
  ggtitle("Stc-ww G2") + 
  my_theme + 
  ylim(c(0,3.5)) +
  ylab("") + 
  xlab("Date") + 
  theme(legend.position = "none")
G2_stc_plot_posterior_rt
```
